The \dealii{} Library, Version 9.2

### 2020-06-02 9.2/paper.tex
Add one acknowledgment.

As part of this effort, we ran benchmarks on the TACC Frontera system, where we were able to apply the matrix-free geometric multigrid framework to a variable viscosity Stokes system and achieved weak and strong scaling up to 114k MPI ranks with up to
\num{2.1e11} unknowns. This is likely the currently largest block system solved with \dealii{} and required various optimizations
and fixes on top of the ones mentioned above:
(i) Bug fixes to concurrent point to point communications.
(ii) Fixes multigrid transfer with adaptive refinement and more than \num{4e9} unknowns.
(iii) Fixes to index sets in block indices with more than \num{4e9} unknowns.
(iv) Fixes to computations with more than \num{4e9} active cells.
(v) Implementation of IDR(s) solvers to reduce memory overhead.
For more details, see \cite{clevenger_stokes19}.

@@

  \item \texttt{step-50} is a program that demonstrates the parallel geometric multigrid features
  in \dealii{} as described in \cite{ClevengerHeisterKanschatKronbichler2019}.
  The problem considered is a variable viscosity Laplace equation and it is solved
  with three different approaches:
  (i) With a matrix-based geometric multigrid based on Trilinos or
  PETSc; (ii) with a matrix-free
  geometric multigrid; (iii) using algebraic multigrid (Trilinos ML).

  \todo[inline]{Timo/Conrad/... to write}

@@

W.~Bangerth and T.~Heister were also partially supported by award DMS-1821210.
\todo[inline]{Need to add FRES project}

>>>>

As part of this effort, we ran benchmarks on the TACC Frontera system, where we were
able to apply the matrix-free geometric multigrid framework to a variable viscosity
Stokes system and achieved weak and strong scaling up to 114K MPI ranks with up to
\num{2.1e11} unknowns. This is likely the largest block system currently solved with
\dealii{} and required various optimizations
and fixes on top of the ones mentioned above:
(i) Bug fixes to concurrent point to point communications.
(ii) Fixes multigrid transfer with adaptive refinement and more than \num{4e9} unknowns.
(iii) Fixes to index sets in block indices with more than \num{4e9} unknowns.
(iv) Fixes to computations with more than \num{4e9} active cells.
(v) Implementation of IDR(s) solvers to reduce memory overhead.
For more details, see \cite{clevenger_stokes19}.

@@

  \item \texttt{step-50} is a program that demonstrates the parallel geometric multigrid features
  in \dealii{} as described in \cite{ClevengerHeisterKanschatKronbichler2019}.
  The problem considered is a variable viscosity Laplace equation and it is solved
  with three different approaches:
  (i) using a matrix-based geometric multigrid based on Trilinos or
  PETSc; (ii) using a matrix-free
  geometric multigrid; (iii) using algebraic multigrid (Trilinos ML). The tutorial
  demonstrates the superiority of the matrix-free method for the problem under consideration,
  and shows that, for matrix-based formulations, the performance of algebraic and
  geometric multigrid methods are roughly comparable.

@@

W.~Bangerth and T.~Heister were also partially supported by award DMS-1821210
and EAR-1925595.
